Video Understanding : A review of action detection-recognition dataset

### 2024-02-19 paper.tex
added kinetics + epic kitchens

In the version 1.3 released in Mar 2016, ActivityNet contains 849 hours from 27,801 videos of indoor actions with a total of 68.8 hours that appear 203 human-centric activities. Most of the videos have lengths ranging from 5 to 10 minutes at 30 FPS have HD resolution quality (1280x720). 
\subsection{Youtube-8M}
In 2016, YouTube-8M \cite{YouTube8M} was introduced as the largest multi-label video classification dataset, which utilized the content-based annotation method. Unlike previous datasets such as Sports-1M \cite{Sports1M} and ActivityNet \cite{ActivityNet}, which only assigned a limited number of action categories, YouTube-8M employed Knowledge Graph entities to filter topics presented on YouTube and therefore broadening the scope to cover a wide range of activities. The purpose of this dataset is to understand the main actions in the video and summarize them into key topics.

@@

\subsection{Something Something}
Introduced its first version in 2017, Something V1 \cite{somethingsomething} emphasizes detailed interactions between human actions and objects, aiming to provide fine-grained videos that reflect real-world aspects. The YouTube-sourced datasets, such as Sport-1M \cite{Sports1M} or YouTube-8M \cite{YouTube8M}, although notably large in size, still involve combining features extracted from frames, thus becoming a "set of images" classification task.

@@

In the newer V2 version released in 2018, the number of videos has increased to 220,847 clips, which is twice the number in V1, while retaining the same set of labels totaling 174. Additionally, each clip has been upgraded to a quality of 240px. Each clip has an average length of 2-6 seconds performing a single action at 12 FPS. Overall, there are 318,572 annotations, which involve 30,408 unique objects. 
\subsection{Charades}
Introduced in 2016, Charades \cite{Charades} is described as "Hollywood in Homes" when using a man-made dataset instead of downloading videos from YouTube. Using a similar method to the Something \cite{somethingsomething} dataset, a group of AMT workers was hired to employ the Hollywood filming method to create clips from diverse environments. Due to the noisy labels and background context from datasets sourced from the internet, such as HMDB51 \cite{HMDB51} and UCF101 \cite{UCF101}, Charades aims to create a high-quality and realistic dataset, particularly focusing on daily activities.

The dataset comprises of 9,848 videos with an average length of 30 seconds, which demonstrates 157 action classes and 46 object classes. Overall, there are 27,847 video descriptions and 66,500 temporally localized action contributed by 267 people.

\subsection{AVA}
Introduced in 2018, AVA's \cite{AVA} main goal is to overcome weaknesses of previous datasets like Sports-1M \cite{Sports1M}, YouTube-8M \cite{YouTube8M}, Something Something \cite{somethingsomething}, and Moments in Time \cite{momentsintime}, which focus on large-scale datasets and are often annotated automatically, leading to noisy annotations. Other datasets such as ActivityNet \cite{ActivityNet}, THUMOS \cite{THUMOS}, and Charades utilize a large number of videos containing multiple actions but only provide temporal annotations. Therefore, AVA provides realistic fine-grained recognition in a complex environment where actors perform a set of combined actions, aiming to enhance spatio-temporal action localization.

Currently, there are four different versions of AVA. The newest version, v2.2, consists of a total of 430 videos covering 80 classes extracted from movies. Each video contributes 15 minutes of footage sampled at a rate of 1Hz, which translates to one frame per second, resulting in 897 segments per 15 minutes.
\subsection{Moments in Time}
In 2019, Moments in Time \cite{momentsintime} was introduced and became one of the largest datasets comprising hundreds of verbs depicting moments lasting a few seconds. Over the years, the rapid growth of datasets has expanded the usability of human action understanding. Large-scale video datasets such as Kinetics and YouTube-8M \cite{YouTube8M} play significant roles in studying open-world vocabulary from the internet. Other datasets, such as ActivityNet \cite{ActivityNet} and AVA \cite{AVA}, explore recognizing and localizing fine-grained actions by linking correlations. To enhance these characteristics, Moments in Time aims to ensure a high-quality and balanced dataset, capturing both inter- and intra-class variations across different levels of abstraction for video understanding.

>>>>

In the version 1.3 released in Mar 2016, ActivityNet contains 849 hours from 27,801 videos of indoor actions with a total of 68.8 hours that appear 200 human-centric activities. Most of the videos have lengths ranging from 5 to 10 minutes at 30 FPS have HD resolution quality (1280x720). 
\subsection{Youtube-8M}
In 2016, YouTube-8M \cite{YouTube8M} was introduced as the largest multi-label video classification dataset, which utilized the content-based annotation method. Unlike previous datasets such as Sports-1M \cite{Sports1M} and ActivityNet \cite{ActivityNet}, which only assigned a limited number of action categories, YouTube-8M employed Knowledge Graph entities to filter topics presented on YouTube and therefore broadening the scope to cover a wide range of activities. The purpose of this dataset is to understand the main actions in the video and summarize them into key topics.

@@

\subsection{Charades}
Introduced in 2016, Charades \cite{Charades} is described as "Hollywood in Homes" when using a man-made dataset instead of downloading videos from YouTube. Using a similar method to the Something \cite{somethingsomething} dataset, a group of AMT workers was hired to employ the Hollywood filming method to create clips from diverse environments. Due to the noisy labels and background context from datasets sourced from the internet, such as HMDB51 \cite{HMDB51} and UCF101 \cite{UCF101}, Charades aims to create a high-quality and realistic dataset, particularly focusing on daily activities.

The dataset comprises of 9,848 videos with an average length of 30 seconds, which demonstrates 157 action classes and 46 object classes. Overall, there are 27,847 video descriptions and 66,500 temporally localized action contributed by 267 people.
\subsection{Something Something}
Introduced its first version in 2017, Something V1 \cite{somethingsomething} emphasizes detailed interactions between human actions and objects, aiming to provide fine-grained videos that reflect real-world aspects. The YouTube-sourced datasets, such as Sport-1M \cite{Sports1M} or YouTube-8M \cite{YouTube8M}, although notably large in size, still involve combining features extracted from frames, thus becoming a "set of images" classification task.

@@

In the newer V2 version released in 2018, the number of videos has increased to 220,847 clips, which is twice the number in V1, while retaining the same set of labels totaling 174. Additionally, each clip has been upgraded to a quality of 240px. Each clip has an average length of 2-6 seconds performing a single action at 12 FPS. Overall, there are 318,572 annotations, which involve 30,408 unique objects. 
\subsection{Kinetics}
In 2017, one of the most famous action classification datasets, Kinetics, was introduced. Its method combines elements from the previous HMDB51 \cite{HMDB51} and UCF101 \cite{UCF101}datasets and expands the number of action classes to 400. By collecting videos from YouTube, the dataset can capture various camera motions, angles, lighting conditions, etc., and therefore covering a broad range of human actions.

Later in 2018, an updated version, Kinetics-600, was introduced. Kinetics-600 is a superset of Kinetics-400, retaining the original 368 classes and splitting 32 classes to provide clearer explanations. Additionally, a new filtering method was used to gather videos correlated to the action classes. Due to some validation sets from Kinetics-400 becoming part of the Kinetics-600 test set, it is recommended not to evaluate Kinetics-600 with a pre-trained Kinetics-400 model.

In 2020, Kinetics-700-2020 was introduced, expanding by 30\% compared to Kinetics-600. Additional actions were sourced partly from EPIC-Kitchens and AVA datasets. Rare actions were gathered from more videos, and duplicated videos were removed. These changes resulted in a more balanced dataset.

The Kinetics dataset contains 10 seconds short clips demonstrating the mentioned action. The table below shows the size of the three Kinetics version:
\subsection{AVA}
Introduced in 2018, AVA's \cite{AVA} main goal is to overcome weaknesses of previous datasets like Sports-1M \cite{Sports1M}, YouTube-8M \cite{YouTube8M}, Something Something \cite{somethingsomething}, and Moments in Time \cite{momentsintime}, which focus on large-scale datasets and are often annotated automatically, leading to noisy annotations. Other datasets such as ActivityNet \cite{ActivityNet}, THUMOS \cite{THUMOS}, and Charades utilize a large number of videos containing multiple actions but only provide temporal annotations. Therefore, AVA provides realistic fine-grained recognition in a complex environment where actors perform a set of combined actions, aiming to enhance spatio-temporal action localization.

Currently, there are four different versions of AVA. The newest version, v2.2, consists of a total of 430 videos covering 80 classes extracted from movies. Each video contributes 15 minutes of footage sampled at a rate of 1Hz, which translates to one frame per second, resulting in 897 segments per 15 minutes.

\subsection{EPIC-KITCHENS}
Since its first introduction in 2018, EPIC-KITCHENS (2020) now extends to provide a fully version of a large-scale egocentric dataset. Recently, ATM workers are being frequently utilized to collect desired video footage scripted scenarios, resulting in great contributions to projects like Something Something \cite{somethingsomething} and Hollywood in Home \cite{Charades}. However, this practice also leads to a lack of natural actions in real life. Given that situation, EPIC-KITCHENS captures random multitasking actions performed by real individuals without any scripts. By recording daily kitchen activities from the first-person perspective of 32 participants from 10 different countries, it aims to present a challenging real-life scenario.

The number of records in the dataset amounts to 55 hours in length. Within it, 39,596 action segments and 454,158 object bounding boxes are extracted. Recorded with GoPro devices, the clips are captured in Full HD resolution at 60 FPS, resulting in 11.5 million frames. The average length of each clip is 1.7 hours, starting from the moment the actor goes to their kitchen and ending when they finish their work, describing both the preparation and cooking process. After that, both objects and actions were annotated manually.

\subsection{Moments in Time}
In 2019, Moments in Time \cite{momentsintime} was introduced and became one of the largest datasets comprising hundreds of verbs depicting moments lasting a few seconds. Over the years, the rapid growth of datasets has expanded the usability of human action understanding. Large-scale video datasets such as Kinetics and YouTube-8M \cite{YouTube8M} play significant roles in studying open-world vocabulary from the internet. Other datasets, such as ActivityNet \cite{ActivityNet} and AVA \cite{AVA}, explore recognizing and localizing fine-grained actions by linking correlations. To enhance these characteristics, Moments in Time aims to ensure a high-quality and balanced dataset, capturing both inter- and intra-class variations across different levels of abstraction for video understanding.
